---
title: "class10-work"
author: "isha mukundan"
format: html
editor: visual
---

## Midterm Project

Dataset: USDA-NASS Strawberries

```{r}
#| label: load libraries
#| warning: false
#| message: false

library(knitr)  
library(kableExtra)
library(tidyverse)
library(stringr)
```

```{r}
#| label: read data

strawberry <- read_csv("straw1.csv", col_names = TRUE)

glimpse(strawberry)
```

Check what all types of values are under Program (if only Survey it can be removed).

Check what all types of values are under Geo Level (if only State it can be removed).

Check if Week Ending, Ag District, Ag District Code, County, County ANSI, Zip Code, Region, Watershed, and CV are all NA?

```{r}
unique(strawberry$Program)

unique(strawberry$`Geo Level`)

unique(strawberry$`Week Ending`)
unique(strawberry$`Ag District`)
unique(strawberry$`Ag District Code`)
```

Write a function to determine what values are present in each column.
```{r}
strawberry_vals <- list() # initialize strawberry_vals as a list

for(i in 1:dim(strawberry)[2]) {
  strawberry_vals[[i]] <- unique(strawberry[,i])
}
```

